manuscript

### 2022-09-23 ms/manuscript.Rmd
update ms with citations

Finally, we found that community competence and host abundance correlated positively with prevalence while mean water temperature correlated negatively with prevalence. In separate univariate analyses when using a Spearman rank correlation test we found significant results for community competence (P < 0.0001; figure 5), abundance (P < 0.01; figure 5), and mean water temperature (P = 0.021; figure 5) after adjusting for multiple comparisons using the “Holm” method [@2] (Aickin & Gensler, 1996; Holm, 1979). Due to the inherently noisy data on parasite prevalence, a multivariate model that predicted infection prevalence in response to community competence, total host abundance, and mean water temperature was not able to detect any significant relationships. Overall, these results suggest that the prevalence of ranavirus in a community may be driven by multiple factors working in conjunction and support our predictions regarding the directional effects of community competence, host abundance, and virus half-life (Figure 5). Species richness was not predictive of infection prevalence meaning we did not detect a classic dilution effect pattern given by a negative relationship; rather the non-significant trend was slightly positive (Supplementary Figure 5; Spearman’s rho = 0.15, P = 0.14).

>>>>

Finally, we found that community competence and host abundance correlated positively with prevalence while mean water temperature correlated negatively with prevalence. In separate univariate analyses when using a Spearman rank correlation test we found significant results for community competence (P < 0.0001; figure 5), abundance (P < 0.01; figure 5), and mean water temperature (P = 0.021; figure 5) after adjusting for multiple comparisons using the “Holm” method [@aickin_adjusting_1996; @holm_simple_1979]. Due to the inherently noisy data on parasite prevalence, a multivariate model that predicted infection prevalence in response to community competence, total host abundance, and mean water temperature was not able to detect any significant relationships. Overall, these results suggest that the prevalence of ranavirus in a community may be driven by multiple factors working in conjunction and support our predictions regarding the directional effects of community competence, host abundance, and virus half-life (Figure 5). Species richness was not predictive of infection prevalence meaning we did not detect a classic dilution effect pattern given by a negative relationship; rather the non-significant trend was slightly positive (Supplementary Figure 5; Spearman’s rho = 0.15, P = 0.14).
